API design for machine learning software: experiences from the scikit-learn project

### 2013-08-09 paper.tex
Address larsmans comment

From the start, the choice to let a single object serve dual purpose as
estimator and model has mostly been driven by usability and technical
considerations. From the user point of view, having two coupled instances (i.e.,
an estimator object, used as a factory, and a model object, produced by the
estimator) indeed decreases the ease of use and is also more likely to
unnecessarily confuse newcomers. From the developer point of view, decoupling
estimators from models also creates parallel class hierarchies and increases the
overall maintenance complexity of the project. For these practical reasons, we
believe that decoupling estimators from models is not worth the effort. The good
reason for decoupling however, would be that it makes it possible to ship a
model in a new environment without having to deal with potentially complex
software dependencies. Such a feature could however still be implemented in
\sklearn by making estimators able to export a fitted model to an agnostic model
description such as PMML~\citep{guazzelli2009pmml}.

>>>>

From the start, the choice to let a single object serve dual purpose as
estimator and model has mostly been driven by usability and technical
considerations. From the user point of view, having two coupled instances (i.e.,
an estimator object, used as a factory, and a model object, produced by the
estimator) indeed decreases the ease of use and is also more likely to
unnecessarily confuse newcomers. From the developer point of view, decoupling
estimators from models also creates parallel class hierarchies and increases the
overall maintenance complexity of the project. For these practical reasons, we
believe that decoupling estimators from models is not worth the effort. A good
reason for decoupling however, would be that it makes it possible to ship a
model in a new environment without having to deal with potentially complex
software dependencies. Such a feature could however still be implemented in
\sklearn by making estimators able to export a fitted model, using the
information from its public attributes, to an agnostic model description such as
PMML~\citep{guazzelli2009pmml}.
